### 2022-03-18 paper/localpsf.tex
restructuring paper

MOMENTS PERMIT IMPROVED INTERPOLATION. IMPROVED INTERPOLATION REQUIRES H-MATRIX. H-MATRIX WITH IMPROVED INTERPOLATION ALSO SOLVES BOUNDARY ARTIFACT PROBLEM. ALSO DOESNT REQUIRE REGULAR GRID. ALSO SCALABLE TO LARGE NUMBER OF IMPULSE RESPONSES. FFT HAS FAST MATVEC BUT NOT OTHER OPTIONS.

Conventional H-matrix construction methods require access to matrix entries of the matrix being approximated, and therefore cannot be used to efficiently form H-matrix approximations of operators that are only available through matrix-vector products. There are matrix-free methods for H-matrix approximation \cite{LEXINGPEELINGPROCESS}, and these methods have been used to form H-matrix representations of Hessians in PDE constrained inverse problems \cite{ILONAHMATRIX,NOEMIHMATRIX}. While these matrix-free H-matrix construction methods are asymptotically scalable in theory, the required number of matrix vector products can be large in practice.

>>>>

%MOMENTS PERMIT IMPROVED INTERPOLATION. IMPROVED INTERPOLATION REQUIRES H-MATRIX. H-MATRIX WITH IMPROVED INTERPOLATION ALSO SOLVES BOUNDARY ARTIFACT PROBLEM. ALSO DOESNT REQUIRE REGULAR GRID. ALSO SCALABLE TO LARGE NUMBER OF IMPULSE RESPONSES. FFT HAS FAST MATVEC BUT NOT OTHER OPTIONS.

Since we are building an H-matrix approximation of $\Aop$, it is natural to ask why we need to go through an elaborate process to compute impulse responses and interpolate them. Can we build the H-matrix directly? In short, no, not efficiently. The reason is that classical H-matrix construction methods \cite{HMATRIXCONSTRUCTION} require access to matrix entries of the matrix being approximated, and therefore cannot be used to efficiently form H-matrix approximations of operators that are only available through matrix-vector products. Our impulse response interpolation lets us quickly compute approximations to matrix entries, which allows us to use these classical H-matrix construction methods. There are newer matrix-free methods for H-matrix approximation based on the so-called ``peeling process'' \cite{LEXINGPEELINGPROCESS}, and these methods have been used to form H-matrix representations of Hessians in PDE constrained inverse problems \cite{ILONAHMATRIX,NOEMIHMATRIX}. While these matrix-free H-matrix construction methods are asymptotically scalable in theory, from a practical point of view the required number of matrix vector products is unreasonably large. Matrix-free H-matrix construction methods are currently a topic of considerable research, so future algorithmic improvements may make these methods more feasible in the future.
